---
title: "Prima squadra"
format:
  html:
    theme: darkly
    css: styles.css
---


```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

source("code/data_generation_ft.R")

```

Questa è la sezione dedicata alla **prima squadra**.

## Portieri
- K. Ferrara 1  
- C. Maianti 12  

## Difensori
- [A. Arpini](GiocatoriFT/arpini.html)
- [S. Azzali](GiocatoriFT/azzali.html) 
- [V. Camilleri](GiocatoriFT/camilleri.html) 
- [E. Maccherini](GiocatoriFT/maccherini.html)  
- [L. Niculae](GiocatoriFT/niculae.html)
- [M. Vailati](GiocatoriFT/vailati.html)

## Centrocampisti
- [N. Abba](GiocatoriFT/abba.html)
- [J. Cerasani](GiocatoriFT/cerasani.html)
- [T. Erman](GiocatoriFT/erman.html)
- [L. Gramignoli](GiocatoriFT/gramignoli.html)
- [A. Latini](GiocatoriFT/latini.html)
- [J. Mozzanica](GiocatoriFT/mozzanica.html)
- [R. Pavesi](GiocatoriFT/pavesi.html)
- [T. Serioli](GiocatoriFT/serioli.html)
- [R. Tomella](GiocatoriFT/tomella.html)
- [T. Valdameri](GiocatoriFT/valdameri.html)

## Attaccanti
- [E. Neci](GiocatoriFT/neci.html)
- [G. Recino](GiocatoriFT/recino.html)
- [D. Fenotti](GiocatoriFT/fenotti.html) 
- [M. Varisco](GiocatoriFT/varisco.html)

# Analisi All Time

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

source("code/ReportUno.R")
source("code/ReportDue.R")
source("code/fisico_vs_tecnica.R")
source("code/data_passes.R")
source("code/scatter_ruoli.R")

scatter_phy_tec


```

::: {.panel-tabset}
# Full Sessions
```{r, echo=FALSE, message=FALSE, warning=FALSE}
scatter_pass_regain
```

# Partita Finale 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
scatter_pass_regain_part
```

:::

::: {.panel-tabset}
# Difensori
```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-format: png
#| fig-dpi: 320
#| fig-bg: "#0b0b0b"
#| fig-width: 7
#| fig-height: 7
#| out-width: "85%"

scatter_dif
```

# Centrocampisti 
```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-format: png
#| fig-dpi: 320
#| fig-bg: "#0b0b0b"
#| fig-width: 7
#| fig-height: 7
#| out-width: "85%"

scatter_cc
```

# Attaccanti 
```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-format: png
#| fig-dpi: 320
#| fig-bg: "#0b0b0b"
#| fig-width: 7
#| fig-height: 7
#| out-width: "85%"

scatter_att
```

:::


```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("code/carichi_lavoro.R")

tb_carichi_lavoro
```


# Rankings

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("code/ReportUno.R")
source("code/ReportUno.R")
source("code/Rankings.R")

```

::: {.columns}

::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_topspeed
```

:::
::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_workrate
```

::: 

::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_touches
```

:::
::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_releases
```
:::


