---
title: "Prima squadra"
format:
  html:
    theme: darkly
    css: styles.css
---


Questa è la sezione dedicata alla **prima squadra**.

## Portieri
- K. Ferrara 1  
- C. Maianti 12  

## Difensori
- [A. Arpini](GiocatoriFT/arpini.html)
- [S. Azzali](GiocatoriFT/azzali.html) 
- [E. Bettinelli](GiocatoriFT/bettinelli.html)  
- [V. Camilleri](GiocatoriFT/camilleri.html) 
- [E. Maccherini](GiocatoriFT/maccherini.html)  
- [M. Vailati](GiocatoriFT/vailati.html)

## Centrocampisti
- [N. Abba](GiocatoriFT/abba.html)
- [L. Gramignoli](GiocatoriFT/gramignoli.html)
- [A. Latini](GiocatoriFT/latini.html)
- [J. Mozzanica](GiocatoriFT/mozzanica.html)
- [R. Pavesi](GiocatoriFT/pavesi.html)
- [F. Russo](GiocatoriFT/russo.html)
- [T. Serioli](GiocatoriFT/serioli.html)
- [R. Tomella](GiocatoriFT/tomella.html)

## Attaccanti
- [R. De Martino](GiocatoriFT/demartino.html)
- [B. Diop](GiocatoriFT/diop.html)
- [D. Fenotti](GiocatoriFT/fenotti.html) 
- [M. Varisco](GiocatoriFT/varisco.html)

# Analisi All Time

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

source("code/ReportUno.R")
source("code/ReportDue.R")
source("code/fisico_vs_tecnica.R")
source("code/data_passes.R")

scatter_phy_tec


```

::: {.panel-tabset}
# Full Sessions
```{r, echo=FALSE, message=FALSE, warning=FALSE}
scatter_pass_regain
```

# Partita Finale 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
scatter_pass_regain_part
```

:::


```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("code/carichi_lavoro.R")

tb_carichi_lavoro
```


# Rankings

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("code/ReportUno.R")
source("code/ReportUno.R")
source("code/Rankings.R")

```

::: {.columns}

::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_topspeed
```

:::
::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_workrate
```

::: 

::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_touches
```

:::
::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_releases
```
:::


