---
title: "Prima squadra"
format:
  html:
    theme: darkly
    css: styles.css
---


Questa è la sezione dedicata alla **prima squadra**.

## Portieri
- K. Ferrara 1  
- C. Maianti 12  

## Difensori
- A. Arpini 2
- S. Azzali 3  
- E. Bettinelli 4  
- V. Camilleri 5 
- E. Maccherini 13  
- M. Vailati 14

## Centrocampisti
- [N. Abba 6](GiocatoriFT/abba.html)
- L. Gramignoli 7
- A. Latini 8
- J. Mozzanica 10
- R. Pavesi 18
- F. Russo 15
- T. Serioli 16
- R. Tomella 17

## Attaccanti
- R. De Martino 9
- B. Diop 11  
- D. Fenotti 19
- M. Varisco 20

# Analisi All Time

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

source("code/ReportUno.R")
source("code/ReportDue.R")
source("code/fisico_vs_tecnica.R")


scatter_phy_tec


```


# Rankings

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("code/ReportUno.R")
source("code/ReportUno.R")
source("code/Rankings.R")

```

::: {.columns}

::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_topspeed
```

:::
::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_workrate
```

::: 

::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_touches
```

:::
::: {.column width="50%"}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tb_releases
```


# Advanced Analytics
