---
title: "Under 17"
format:
  html:
    theme: darkly
    css: styles.css
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

source("code/data_generation_ft.R")
source("code/data_generation_u19.R")
source("code/data_generation_u17.R")

```


Questa è la sezione dedicata alla **Under 17**.

## Portieri
- A. Ajdini
- A. Laini
- A. Riboli

## Difensori
- [M. Bresciani](GiocatoriU17/bresciani.html)
- [A. Brusati](GiocatoriU17/brusati.html)
- [E. Di Cicco](GiocatoriU17/dicico.html)
- [A. Granata]
- [P. Marelli](GiocatoriU17/marelli.html)
- [A. Mhilli](GiocatoriU17/mhilli.html)
- [S. Montoya](GiocatoriU17/montoya.html)
- [R. Nicolini](GiocatoriU17/nicolini.html)

## Centrocampisti
- [K. Gagliardi](GiocatoriU17/gagliardi.html)
- [F. Massazza](GiocatoriU17//massazza.html)
- [F. Moruzzi](GiocatoriU17/moruzzi.html)
- [L. Pascale](GiocatoriU17/pascale.html)
- [D. Pea](GiocatoriU17/pea.html)
- [D. Shiku](GiocatoriU17/shiku.html)
- [M. Vanelli](GiocatoriU17/vanelli.html)

## Attaccanti
- [T. Calia](GiocatoriU17/calia.html)
- [L. Kurici](GiocatoriU17/kurici.html)
- [M. Laini](GiocatoriU17/laini.html)
- [F. Ndema](GiocatoriU17/ndema.html)
- [M. Tacchini]

# Analisi All Time


## Carichi di Lavoro

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

source("code/carichi_lavoro.R")
tb_carichi_lavoro_u17

```


## Statistiche all time
```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

source("code/phy_vs_tech_new.R")
ctx <- readRDS(here::here("data", "derived", "u17_context.rds"))
plot_phy_tec_squad(ctx$scatter_u17)

```


## Classifiche fisiche

::: columns

::: {.column width="50%"}
```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

source("code/Rankings_u17.R")
tb_topspeed

```
:::

::: {.column width="50%"}
```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

tb_workrate

```
:::

::: 


## Classifiche Tecniche 

::: columns

::: {.column width="50%"}
```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

tb_touches

```
:::

::: {.column width="50%"}
```{r, echo=FALSE, message=FALSE, warning=FALSE, error=TRUE}

tb_releases

```
:::

:::

## Premio tesseramenti 
[Premio tesseramenti]("tesseramenti_u17.html")
